\documentclass[PhD]{uclathes}

\input{preamble/preamble.tex}

\title{
	Search for Long-Lived Particles Decaying to Photon Pairs in Rare Higgs Boson Decays using 13 TeV Proton-Proton Collisions at the Compact Muon Solenoid
}

\author{Tyler Christopher Lam}
\department{Physics}
\degreeyear{2024}

\chair{Michalis Bachtis}
\member{Davlid Saltzberg}
\member{Jay Hauser}
\member{Thomas Dumitrescu}
\dedication{
	\textit{
		To my parents, Jean and Bobby, for their love and support from across the country
	}
}

\acknowledgments{
First and foremost, no one has contributed more to my success as a graduate student than my advisor, Michalis Bachtis. The first summer I spent researching for him cemented my desire to study experimental particle physics. From there, his dedication, enthusiasm, and mentorship were indispensable during my journey through graduate school.  I do not know of any advisor who is more available to their students and is more willing to perform hands-on work to help in a project. Thank you for everything, Michalis.

More thanks goes to the current and former members of the UCLA CMS research group. Thank you to my former officemates David Hamilton and Maxx Tepper; our workplace shenanigans gave me something to look forward to during slow days at work. I would also like to thank the other CMS graduate students from when I arrived at UCLA: Brent Stone, Will Nash, and Chris Schnaible for welcoming me into the group and our countless thought-provoking lunch discussions. Lastly, a thanks to the remaining graduate students, engineers, and postdocs Gael Flores-Avila, Antonett Prado, Abhishek Datta, Elisabetta Manca, Joseph Carlson, David Gotler, Alex Tan, and Delano Campos for making the office an enjoyable place to work.

My time at UCLA has been marked by countless friendships with students outside of the CMS research group as well. No words can express how important my former roommates Adam Trapp and Kyle Ferguson were towards maintaining my sanity during a global pandemic. Despite everything, I look back on our many (mis)adventures and remember this time fondly. You have been such an integral part of my time at UCLA that, to avoid repetition, I ask that put yourselves in any of the following thanks that apply to you. In a similar vein, thank you to Ronald Lopez and Rick Mebane for the weekly tennis sessions, which gave me an excuse to go outside during the lockdown. I would also like to thank Eric Cropp, Eddie Chang, Lukas Lindwasser, and Pratik Sathe for turning our comprehensive exam study group into a food-centric outing group.  To my friends that I have bonded with on the bouldering wall, I would like to thank Tony Pahl, Abhijah Simon, Akash Gupta, Rory Bentley, Will Flanagan, and Wes Armstrong. Finally, for making after-work and weekend board game nights fun I would like to thank Sarah Chase, Henry Wong, and Phil Travis.

Beyond UCLA, I would like to thank my parents, Bobby and Jean, who eventually learned not to ask a graduate student when they will graduate. My career as a physicist would never have been possible without them. Thank you to my sibling Ira for being a consistent moral and political compass. Additional thanks to Tor Raubenheimer -- my uncle, Stanford professor, and physicist at SLAC -- who inspired me to study physics in middle school when he joined our family. Last, but by no stretch of the imagination least, thank you to Levina Lin for being an unending source of stability and support over the last few years.

This thesis includes material that is based upon work supported by the U.S. Department of Energy under award number DE-SC0009937.
}

\vitaitem{2017}
{
	B.S\ (Physics) and B.A.\ (Mathematics),
	University of Virginia
}

\vitaitem{2017-2018}
{
	Teaching Assistant,
	Department of Physics and Astronomy,
	UCLA,
	Los Angeles, California
}

\vitaitem{2018}
{
	M.S.\ (Physics)
	UCLA
}

\vitaitem{2018-2024}
{
	Graduate Research Assistant,
	Department of Physics and Astronomy,
	UCLA
}

\abstract{
This thesis describes the search for rare Standard Model (SM) Higgs boson decays to long-lived scalar bosons ($\Phi$) decaying to photon pairs using data collected by the Compact Muon Solenoid (CMS) detector at the Large Hadron Collider. The data were collected from 2016, 2017, and 2018 proton-proton collisions at center-of-mass energy of $\sqrt{s}=13\TeV$ and correspond to an integrated luminosity of $138\unit{fb^{-1}}$. Events are triggered using the leptonic decays of the \PZ boson produced in association with the SM Higgs boson. Although the CMS electromagnetic calorimeter has limited vertex reconstruction capabilities for photons, this analysis utilizes a novel reconstruction technique using kinematic constraints to calculate the displaced vertices of the diphotons. Signal is extracted using a counting-based maximum-likelihood approach in bins of the diphoton vertex \lxy and the invariant photon mass. Results are interpreted in terms of upper limits on branching ratios $\mathcal{BR}(\PH\to\Phi\Phi)\times\mathcal{BR}(\Phi\to\PGg\PGg)$ and in terms of the model independent production cross section $\sigma(\PZ+\Phi\Phi)\times\mathcal{BR}(\Phi\to\PGg\PGg)$. No significant excess above SM expectation is observed.
}

\begin{document}

\makeintropages

\input{chapters/01_intro.tex}
\input{chapters/02_theory.tex}
\input{chapters/03_experiment.tex}
\input{chapters/04_muons.tex}
\input{chapters/05_analysis.tex}
\begin{appendices}
	\input{chapters/A1_QFT.tex}
\end{appendices}
\bibliography{bib/articles,bib/misc,bib/books,bib/reports}
\bibliographystyle{unsrturl}

\end{document}